---
title: "Databinders"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

[![Build Status](https://travis-ci.org/ahmad-alkadri/databinders.svg?branch=master)](https://travis-ci.org/ahmad-alkadri/databinders)

## Description

The aim of databinders is to solve a common problem of mine: 
the need for binding many datasets containing the experimental data of my many specimens and recapitulating them into a single dataframe. 

Note that this package was basically written as a wrapper 
of the well-known [rio](https://cran.r-project.org/web/packages/rio/) package. It is a swiss-army package for I/O operations in R 
and also my personal preferred go-to package 
for working with many types of data.

## Installations

To install this package, simply launch `R` in your computer, 
either through the IDE (ex: RStudio) or the terminal, and type:

`devtools::install_github("ahmad-alkadri/databinders")`

Note that if you don't have yet `rio` package installed, 
installing this package will also install `rio` in your R.

## Examples

I've prepared a zipped file containing the Iris dataset, 
separated into three files in excel, csv, and ods format 
based on their species name. You can head over to the folder through this 
[link](https://github.com/ahmad-alkadri/databinders/tree/master/Examples) now 
to check them out. Anyway, this facilitates in showing 
the examples on how this package work. To try it out, just type:

```{r}
library(databinders)

#Download the zipped Examples folder from GitHub
download.file(url = "https://github.com/ahmad-alkadri/databinders/raw/master/Examples.zip", 
              destfile = "Examples.zip")

#Unzip the compressed file
unzip(zipfile = "Examples.zip")

#Bind the excel files in the XLSX subrepository
df <- bindall(repo = "Examples/XLSX/", type = "xlsx")

#Print the head() of the dataframe
print(head(df))
```

